Volatility and the Buyback Anomaly: Interactive Tool

### 2016-05-17 index.Rmd
Use a single busy indicator

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = "EU.Index"),
  mainPanel(
    navlistPanel(
      tabPanel("Histogram",
               busyIndicator("Please wait while we load the data for you... This shouldn't take more than a few seconds...",wait = 0),
               renderPlot({
                 feature = DATASET_NEW()$BUYBACK_DATA_TOOL[,which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic)]
                 feature = feature[!is.na(feature)]
                 if (!is.numeric(feature))
                   feature = 1
                 hist(feature, density = 100, breaks = 100)
               })),
      tabPanel("Summary Statistics",
               renderDataTable({
                 feature = DATASET_NEW()$BUYBACK_DATA_TOOL[,which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic)]
                 feature = feature[!is.na(feature)]
                 if (length(unique(feature)) > 20 & is.numeric(feature)){
                   res = t(round(as.matrix(summary(feature)),2))
                   colnames(res) <- c("Minimum", "1st Quantile", "Median", "Mean", "3rd Quantile", "Max")
                 }
                 if (is.character(feature) | length(unique(feature)) <= 20){
                   tmp = table(feature)
                   res = t(as.matrix(tmp))
                 }
                 as.data.frame(res)
                 #m1<-gvisTable(show_data,options=list(showRowNumber=TRUE,width=1220, height=min(400,27*(nrow(show_data)+1)),allowHTML=TRUE,page='disable'))
                 #print(m1,'chart')
               })
      ),
      widths = c(3, 9)),
    style='width: 100%;'))
```

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    navlistPanel(
      tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
               busyIndicator("Calculating results ...",wait = 0),
               renderTable({
                 feature_IRATStable()
               })),
      tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
               busyIndicator("Calculating results ...",wait = 0),
               renderTable({
                 feature_CALtable()
               })),
      tabPanel("Cumulative Abnormal Returns,High, 12m hold",
               busyIndicator("Calculating results ...",wait = 0),
               renderDygraph({
                 pnl_plot_interactive(High_feature_Hedged_react())
               })),
      tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
               busyIndicator("Calculating results ...",wait = 0),
               renderDygraph({
                 pnl_plot_interactive(Low_feature_Hedged_react())
               })),
      tabPanel("Monthly and Yearly Returns, High, 12m hold",
               busyIndicator("Calculating results ...",wait = 0),
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(High_feature_Hedged_react())))
               )),
      tabPanel("Monthly and Yearly Returns, Low, 12m hold",
               busyIndicator("Calculating results ...",wait = 0),
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(Low_feature_Hedged_react())))
               )),
      widths = c(3, 9)),style='width: 100%;'))
```

@@

fluidPage(
  mainPanel(
    navlistPanel(
      tabPanel("Number of Firms per EU Index Value",
               busyIndicator("Calculating results ...",wait = 0),
               renderTable({
                 EU_index_table()
               })),
      tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
               busyIndicator("Calculating results ...",wait = 0),
               renderTable({
                 feature_IRATStable_industry()
               })),
      tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
               busyIndicator("Calculating results ...",wait = 0),
               renderTable({
                 feature_CALtable_industry()
               })),
      widths = c(3, 9)),style='width: 100%;'))
```

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    navlistPanel(
      tabPanel("Histogram of the New Index",
               busyIndicator("Calculating results ...",wait = 0),
               renderPlot({
                 feature = Index_Score_rect()
                 feature = feature[!is.na(feature)]
                 if (!is.numeric(feature))
                   feature = 1
                 hist(feature, density = 100, breaks = 20,main="Index Histogram",xlab="Score")
               })),
      tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
               busyIndicator("Calculating results ...",wait = 0),
               renderTable({
                 feature_IRATStable_index()
               })),
      tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
               busyIndicator("Calculating results ...",wait = 0),
               renderTable({
                 feature_CALtable_index()
               })),
      tabPanel("Cumulative Abnormal Returns,High, 12m hold",
               busyIndicator("Calculating results ...",wait = 0),
               renderDygraph({
                 pnl_plot_interactive(High_feature_Hedged_react_index())
               })),
      tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
               busyIndicator("Calculating results ...",wait = 0),
               renderDygraph({
                 pnl_plot_interactive(Low_feature_Hedged_react_index())
               })),
      tabPanel("Monthly and Yearly Returns, High, 12m hold",
               busyIndicator("Calculating results ...",wait = 0),
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(High_feature_Hedged_react_index())))
               )),
      tabPanel("Monthly and Yearly Returns, Low, 12m hold",
               busyIndicator("Calculating results ...",wait = 0),
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(Low_feature_Hedged_react_index())))
               )),
      widths = c(3, 9)),style='width: 100%;'))
```

>>>>

div(
  style = "width:32px; height:32px; position:fixed; top:0; bottom:0; left:0; right:0; margin: auto; z-index:9999",
  busyIndicator("", wait=111)
)

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = "EU.Index"),
  mainPanel(
    navlistPanel(
      tabPanel("Histogram",
               renderPlot({
                 feature = DATASET_NEW()$BUYBACK_DATA_TOOL[,which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic)]
                 feature = feature[!is.na(feature)]
                 if (!is.numeric(feature))
                   feature = 1
                 hist(feature, density = 100, breaks = 100)
               })),
      tabPanel("Summary Statistics",
               renderDataTable({
                 feature = DATASET_NEW()$BUYBACK_DATA_TOOL[,which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic)]
                 feature = feature[!is.na(feature)]
                 if (length(unique(feature)) > 20 & is.numeric(feature)){
                   res = t(round(as.matrix(summary(feature)),2))
                   colnames(res) <- c("Minimum", "1st Quantile", "Median", "Mean", "3rd Quantile", "Max")
                 }
                 if (is.character(feature) | length(unique(feature)) <= 20){
                   tmp = table(feature)
                   res = t(as.matrix(tmp))
                 }
                 as.data.frame(res)
                 #m1<-gvisTable(show_data,options=list(showRowNumber=TRUE,width=1220, height=min(400,27*(nrow(show_data)+1)),allowHTML=TRUE,page='disable'))
                 #print(m1,'chart')
               })
      ),
      widths = c(3, 9)),
    style='width: 100%;'))
```

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    navlistPanel(
      tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
               renderTable({
                 feature_IRATStable()
               })),
      tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
               renderTable({
                 feature_CALtable()
               })),
      tabPanel("Cumulative Abnormal Returns,High, 12m hold",
               renderDygraph({
                 pnl_plot_interactive(High_feature_Hedged_react())
               })),
      tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
               renderDygraph({
                 pnl_plot_interactive(Low_feature_Hedged_react())
               })),
      tabPanel("Monthly and Yearly Returns, High, 12m hold",
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(High_feature_Hedged_react())))
               )),
      tabPanel("Monthly and Yearly Returns, Low, 12m hold",
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(Low_feature_Hedged_react())))
               )),
      widths = c(3, 9)),style='width: 100%;'))
```

@@

fluidPage(
  mainPanel(
    navlistPanel(
      tabPanel("Number of Firms per EU Index Value",
               renderTable({
                 EU_index_table()
               })),
      tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
               renderTable({
                 feature_IRATStable_industry()
               })),
      tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
               renderTable({
                 feature_CALtable_industry()
               })),
      widths = c(3, 9)),style='width: 100%;'))
```

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    navlistPanel(
      tabPanel("Histogram of the New Index",
               renderPlot({
                 feature = Index_Score_rect()
                 feature = feature[!is.na(feature)]
                 if (!is.numeric(feature))
                   feature = 1
                 hist(feature, density = 100, breaks = 20,main="Index Histogram",xlab="Score")
               })),
      tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
               renderTable({
                 feature_IRATStable_index()
               })),
      tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
               renderTable({
                 feature_CALtable_index()
               })),
      tabPanel("Cumulative Abnormal Returns,High, 12m hold",
               renderDygraph({
                 pnl_plot_interactive(High_feature_Hedged_react_index())
               })),
      tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
               renderDygraph({
                 pnl_plot_interactive(Low_feature_Hedged_react_index())
               })),
      tabPanel("Monthly and Yearly Returns, High, 12m hold",
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(High_feature_Hedged_react_index())))
               )),
      tabPanel("Monthly and Yearly Returns, Low, 12m hold",
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(Low_feature_Hedged_react_index())))
               )),
      widths = c(3, 9)),style='width: 100%;'))
```
